Determining sequence-dependent DNA oligonucleotide hybridization and dehybridization mechanisms using coarse-grained molecular simulation, Markov state models, and infrared spectroscopy

### 2021-09-11 response_letter_2/response_letter.tex

\begin{shaded}
\textbf{Response to Reviewer \# 1}
\end{shaded}

\textcolor{blue}{Recommendation: Publish in JACS without change.
}

\textcolor{blue}{Comments:
Most of my comments were properly addressed. The manuscript, as far as I understand, is suitable for a journal like JACS.
}

\textbf{Author Reply:} We are pleased that the reviewer is satisfied with our modifications and responses and that they are pleased to support publication in JACS. We would like to thank them again for their time, effort, and expert comments.

@@

\textcolor{blue}{
(1) The authors have applied the finite size correction of Ouldridge et al. following a comment by reviewer 2, but it hasn't been applied in the correct way. It would be correct to apply it to the melting curves discussed at the bottom of p7/top of p8. Since the sequences are homodimers, the correction to Tm at the simulation concentration would actually be zero; instead, the widths of transitions would change, as noted by Ouldridge et al.
}

\textcolor{blue}{
However, the authors have actually simulated at 3.5x the experimental conc. If the Ouldridge correction - which assumes ideal behaviour - applies, then it should be relatively simple to correct the curves for the concentration difference. Simply divide the phi ratio by 3.5, and then calculate f\_hybridised using the modified phi. If the Tms were previously too low, this change will make them lower still (perhaps by a couple of K), but it is the fairest comparison. It shouldn't affect the rest of the analysis, although it is worth noting that the simulations were always performed "at the melting temperature for a conc of 7mM" - there is no well-defined, concentration-independent melting temperature.
}

\textcolor{blue}{
However, it is not appropriate to apply the Ouldridge correction to data measuring the dissociation time. The authors effectively measure the statistics of dissociation events in infinite dilution - these are unaffected by the factors that lead to the Ouldridge correction. More specifically, the Ouldridge correction accounts for concentration fluctuations neglected in small, canonical simulations. These concentration fluctuations contribute to the hybridisation rates, not the dissociation rates.
}

%Remove of correction. Report updated text here and in main text and SI using roodr code. Maybe something like ``(We note that although the melting temperature of the homodimer is not affected by the Ouldridge et al. finite size corrections [REF], this empirical correction does account for the higher DNA concentration employed in simulation (7 mM) relative to experiment (2 mM). Although we do not do so here, Owczarzy et al. present a prescription to apply concentration corrections to Tm using knowledge of the enthalpy and entropy of duplex formation and helix nucleation [REF; ``Predicting Sequence- Dependent Melting Stability of Short Duplex DNA Oligomers'' Biopoly 44: 217?239, 1997].''. In your response you can also elaborate on your point of using Eqn. 11 in Ouldridge would fix conc effects at same T but not at new Tm so would need new T ramp or knowledge of dH and dS. Close with saying in any case our empirical correction accounts for these effects plus other uncontrolled effects such as model accuracy etc.

\textbf{Author Reply:} We appreciate these valuable comments and have made several corrections and modifications to the revised manuscript in light of these recommendations.

(I) We thank the reviewer for pointing out that the Ouldridge finite-size fluctuation corrections do not affect the dissociation rates and are therefore not relevant for this comparison. We have eliminated our discussion of this correction at the top of p.~16 in Section 3.1 (``To correct for finite-size effects...'') and modified the plot and caption in Figure 1 to report the original uncorrected data. As mentioned in our previous response letter, the fluctuation correction led to only a slight change in the reported rates and so this modification does not change any of our analysis or interpretations of the data.

It is true that the homodimer finite-size fluctuation correction does not affect the melting temperature but only widens the transition, and this was indeed what we saw when we applied the correction. We have also edited the text on p.~17 that erroneously suggested that this correction would change the dissociation rate or melting temperature:

``The computational time scales and melting temperatures reported in the remainder of the paper are not corrected by these calibration corrections \roodr{\st{or finite-size fluctuations}} since we are only interested in the relative trends in the behaviors of the four sequences.''

(II) We appreciate reviewer's suggestion to be more explicit that melting temperatures are a function of concentration, and that our definition applies to a particular model at a particular concentration. As such we have revised the text in several places to note we are using the melting temperature specific to the 7 mM concentration employed in our simulations:

On page 7:

``each sequence was simulated at its respective melting temperature \roodr{at 7mM concentration as} dictated by the 3SPN.2 model''

On page 9:

`` MSMs were constructed for each of the four DNA sequences \roodr{at their respective 3SPN.2 melting temperatures at 7 mM concentration} from the 40$\times$25 $\mu$s simulation trajectories''

On page 20:

``Since each system is simulated at the \roodr{same 7 mM concentration} and at its respective melting temperature''

(III) We thank the reviewer for the suggestion to correct our simulation prediction of the melting temperature to the experimental concentration. The proposed strategy is to assume ideal behavior, reduce the computed $\phi$ ratio per Eqn.~7 in Ouldridge et al.\ \cite{Ouldridge2010ExtractingSimulations} by the 3.5$\times$ concentration difference, and then recompute $f_{hybridized}$. We believe that this procedure would work under the assumption that the equilibrium constant does not change with temperature, but in general this may not be a good assumption since $-R T_m K_{eq} = \Delta G^\circ = \Delta H^\circ - T_m \Delta S$. Owczarzy et al.\ \cite{Owczarzy1997predicting} engage this issue to develop a van't Hoff-like concentration correction to $T_m$ based on the enthalpies of duplex formation and helix nucleation. In the absence of knowledge of these standard enthalpies, we could instead calculate the melting temperature by performing multiple simulations at a range of temperatures, applying the proposed concentration correction to predict $f_{hybridized}$ at that temperature, then fitting a melting curve from which we could extract the concentration corrected $T_m$. This additional suite of required calculations would be exclusively in service of nailing down the concentration correction and would not change our approach since we intentionally selected the 7 mM 3SPN.2 melting temperature in order to maximize the number of spontaneous transitions between dissociated and hybridized states to provide a rich data set of these events over which to train our MSM.

The approach we take to the concentration correction in the manuscript is an empirical one, wherein we draw a comparison of the computational predictions against experimental measurements. The observed calibration corrections therefore account for net effect of both the 3.5$\times$ higher concentration in simulation and the assumptions and approximations inherent in the 3SPN.2 model. As the reviewer observes, the (+4) K calibration correction encompassing both of these effects is overly optimistic since the concentration corrected $T_m$ will be depressed and controlling for this would require a larger positive correction for the error due to the 3SPN.2 model approximations.

In light of the reviewer's suggestion and the discussion above, we have modified the text on p.~16 to alert the reader to these important issues:

``Although the 3SPN.2 model reproduces melting temperatures relatively well, we observed a systematic 4 K under-prediction relative to experiment and so we apply a universal (+4) K corrective temperature shift to our computational results. \roodr{We note that our simulations are expected to slightly over-predict the melting temperature since they are conducted at 3.5$\times$ higher concentration relative to experiment, and the concentration-adjusted corrective shift accounting for the approximations inherent in the 3SPN.2 model would be slightly larger. Owczarzy et al.\ present an analytical prescription to apply concentration corrections to the melting temperature using knowledge of the enthalpy changes associated with duplex formation and helix nucleation \cite{Owczarzy1997predicting}. In the absence of these quantities, one could instead empirically estimate concentration corrected melting temperatures by conducting a suite of simulations over a range of temperatures and assume ideal molecular behavior to apply concentration corrections to the observed hybridized fractions \cite{Ouldridge2010ExtractingSimulations}. (As demonstrated by Ouldridge et al., finite-size corrections do not affect the melting temperature for homodimers \cite{Ouldridge2010ExtractingSimulations}.) Furthermore, we} note that these empirical calibration factors to the 3SPN.2 predictions are applied only for the purposes of making an experimental comparison, but acknowledge that there are uncertainties introduced by assuming that the equilibrium dynamics at fixed temperature can be compared directly to relaxation kinetics following a 15$^\circ$C T-jump.''

@@

\textcolor{blue}{
(2) I realise now that the criterion for dissociation is that both of the central pairs separate to 1.3nm, which is more reasonable than my previous understanding. However, although the authors say that the estimates of kd\^slow are robust to a range of choices for this cutoff, the yellow, red and green curves all have a noticeable shift between 1.3 and 2.0nm (unsurprisingly blue does not, since the GC pairs are in the core). So what exactly does robust mean? Why not just report the data for larger cutoffs?
}

\textbf{Author Reply:} Our original motivation for selecting a 1.3 nm cutoff was to maintain consistency between that for fraying and dissociation. This is, however, an unnecessary constraint since these are fundamentally different processes. As the reviewer recommends, we now report the data in Figure 1 using the larger 2.0 nm cutoff. We do indeed see relatively small changes in our results upon changing the cutoff from 1.3 nm to 2.0 nm, producing an average change in the calculated values of $k_d^\mathrm{slow}$ of only 7\%, demonstrating that our calculation is robust to the particular choice of cutoff within this range. This modification does not affect any of our subsequent analysis or interpretation.

We have updated the text on p.~15 as follows:

``First, we tracked the slow response corresponding to duplex dissociation in our simulations by compiling the distribution of times at which both of the central base pairs first separate to a distance of \roodr{2.0} nm starting from an initial fully hybridized duplex. This cutoff was selected as the distance beyond \rood{which} the strands are effectively non-interacting and defines the dissociated state. We extracted our computational estimate of $k_d^\mathrm{slow}$ by fitting a decaying exponential to the fraction of hybridized sequences as a function of time $f_\mathrm{hybridized}(t) = \exp(-k_d^\mathrm{slow}t)$. \roodr{We verified that our cutoff was sufficiently large by observing that our calculated values for $k_d^\mathrm{slow}$ changed by an average of only 7\% by adopting a 1.3 nm cutoff.}''

@@

\textcolor{blue}{
(3) In their response to point (7) in my original review, the authors talk about "averaging" over all microstates. Do they mean estimating F as
}

\textcolor{blue}{
F = -kT ln sum\_i  exp(-F\_i/kT)
}

\textcolor{blue}{
where i runs over all microstates in the macrostate? This is very different from averaging F\_i, as might be inferred from the text.
}

\textbf{Author Reply:} Thank you for pointing out our lack of clarity on this point. We have modified the text on p.~S10 of the Supporting Information to more clearly convey the details of this calculation:

\rood{In applying the NN model to each macrostate, we made the simplifying assumption that the ensemble of microstates constituting each macrostate could be represented by a single pattern of Watson-Crick base pairing that are schematically illustrated in Fig.~2a. In reality, each macrostate is composed of an ensemble of microstates that may have slightly different base pairing patterns and explicitly averaging over all of these microstates may change the predictions of the NN model.} \roodr{To evaluate the extent to which the microstate ensembles would change our free energy estimates, we calculated a NN microstate free energy by taking a simple average over the NN free energies predicted for each configuration within a given microstate -- a reasonable assumption given the structural similarity of configurations within a microstate -- then computing macrostate free energies via a weighted average according to the MSM equilibrium occupancy probabilities for each microstate. These operations can be represented as follows, where $i$ indexes over the $N_j$ configurations in microstate $j$, $j$ indexes over microstates, and $p_j$ represents the MSM equilibrium occupancy of microstate $j$,}
\begin{equation}
    F^{micro} = \frac{1}{N_j} \sum_{i \in micro} F_i^{NN} 
\end{equation}
\begin{equation}  
    F^{macro} = \sum_{j \in macro} p_j F_j^{micro}
\end{equation}
Recalculating the NN predictions \roodr{in this way} leads to changes in the $\Delta F = F - F_H$ values reported in Fig.~3 (i.e., the free energy of each macrostate relative to the hybridized state) of $<$1 kJ/mol. As such, representing each macrostate by a single representative microstate and base pairing pattern is a highly accurate simplifying approximation for the purposes of this calculation.

### 2021-09-11 SI.tex
Response 2 Andy edits

\rood{In applying the NN model to each macrostate, we made the simplifying assumption that the ensemble of microstates constituting each macrostate could be represented by a single pattern of Watson-Crick base pairing that are schematically illustrated in Fig.~2a. In reality, each macrostate is composed of an ensemble of microstates that may have slightly different base pairing patterns and explicitly averaging over all of these microstates may change the predictions of the NN model. Recalculating the NN predictions by explicitly averaging over all microstates in the macrostate leads to changes in the $\Delta F = F - F_H$ values reported in Fig.~3 (i.e., the free energy of each macrostate relative to the hybridized state) of $<$1 kJ/mol. As such, representing each macrostate by a single representative microstate and base pairing pattern is a highly accurate simplifying approximation for the purposes of this calculation.}

>>>>

\rood{In applying the NN model to each macrostate, we made the simplifying assumption that the ensemble of microstates constituting each macrostate could be represented by a single pattern of Watson-Crick base pairing that are schematically illustrated in Fig.~2a. In reality, each macrostate is composed of an ensemble of microstates that may have slightly different base pairing patterns and explicitly averaging over all of these microstates may change the predictions of the NN model.} \roodr{To evaluate the extent to which the microstate ensembles would change our free energy estimates, we calculated a NN microstate free energy by taking a simple average over the NN free energies predicted for each configuration within a given microstate -- a reasonable assumption given the structural similarity of configurations within a microstate -- then computing macrostate free energies via a weighted average according to the MSM equilibrium occupancy probabilities for each microstate. These operations can be represented as follows, where $i$ indexes over the $N_j$ configurations in microstate $j$, $j$ indexes over microstates, and $p_j$ represents the MSM equilibrium occupancy of microstate $j$,}
\begin{equation}
    F^{micro} = \frac{1}{N_j} \sum_{i \in micro} F_i^{NN} 
\end{equation}
\begin{equation}  
    F^{macro} = \sum_{j \in macro} p_j F_j^{micro}
\end{equation}
Recalculating the NN predictions \roodr{in this way} leads to changes in the $\Delta F = F - F_H$ values reported in Fig.~3 (i.e., the free energy of each macrostate relative to the hybridized state) of $<$1 kJ/mol. As such, representing each macrostate by a single representative microstate and base pairing pattern is a highly accurate simplifying approximation for the purposes of this calculation.

### 2021-09-11 manuscript.tex
Response 2 Andy edits

All calculations were performed using the LAMMPS simulation package (\url{http://lammps.sandia.gov}) in accordance with best practices for the 3SPN.2 model. \citep{Plimpton1997FastDynamics} A single pair of self-complementary sequences were placed in a cubic periodic box with side length 7.8 nm corresponding to a single-strand concentration of \rood{7 mM}. \rood{This concentration is only 3.5$\times$ larger than the 2 mM concentration employed in our experimental analyses (Section 2.2).} Solvent effects were modeled implicitly by employing Langevin dynamics \citep{DunwegB.Paul1991BrownianNumbers., Bussi2007AccurateDynamics} with an experimentally motivated per-site friction coefficient of 9.94 $\times$ 10$^{-11}$ m$^2$/s. \citep{Nkodo2001DiffusionElectrophoresis, Hinckley2013AnHybridization} We specified a 240 mM implicit salt concentration and treated electrostatic interactions using the Debye-H{\"u}ckel with a 5 nm cutoff radius. \citep{Debye1923ZurElektrolyte} Simulations were performed in the NVT ensemble employing a Langevin thermostat. \citep{Schneider1978Molecular-dynamicsTransitions}. \rood{With the exception of the simulation data reported in Section 3.1 where we draw comparisons against experimental data collected over a range of temperatures,} each sequence was simulated at its \rood{respective melting temperature at 7mM concentration as dictated by the 3SPN.2 model} -- AT-all: 309 K, GC-end: 317 K, GC-core: 324 K, GC-mix: 324 K -- in order to maximize the number of spontaneous transitions between dissociated and hybridized states. Melting temperatures for each sequence were determined empirically by comparing the ratio of hybridized to dissociated populations over a 10 K temperature ramp centered on the nearest neighbor (NN) model predicted melting temperature,~\citep{SantaLucia1998AThermodynamics, Santalucia2004TheMotifs} and selecting the temperature at which the hybridized and dissociated populations were approximately equal. The Langevin equations of motion were integrated using the scheme of Bussi and Parrinello \citep{Bussi2007AccurateDynamics} with a 20 fs integration time step. We performed 40 independent simulations for each of the four sequences with half of the runs initialized from the hybridized state and half from the dissociated state. The initial hybridized state was defined based on the crystal structure coordinates of Arnott et al.~\citep{Arnott1976CRCBiology} The dissociated state was generated from the hybridized state by displacing one strand away from the other by 1 nm in each of the $x$, $y$, and $z$ directions. The magnitude of this displacement did not affect the results so long as all native Watson-Crick (WC) bonds were completely broken. Initial bead velocities were assigned from a Maxwell-Boltzmann distribution at the temperature of interest. Each simulation was conducted for 26 $\mu$s and frames saved to disc every 100 ps. Each simulation required $\sim$24 CPU-hours on 28$\times$Intel E5-2680v4 CPU cores. The first 1 $\mu$s of each run was discarded for equilibration providing us with 40$\times$25 $\mu$s = 1 ms of simulation data for each sequence, during which time we observed 55-100 hybridization/dehybridization events.

@@

To computationally mimic the T-jump process in our 3SPN.2 simulations, we conducted 1 $\mu$s simulations of an initially hybridized DNA duplex over a range of temperatures and monitored its structural relaxation. We performed 120 independent simulations for each DNA sequence at each temperature, and from these extracted computational estimates of $k_d^\mathrm{slow}$ and $k_d^\mathrm{fast}$ (\blauw{Fig.~S4}). First, we tracked the slow response corresponding to duplex dissociation in our simulations by compiling the distribution of times at which both of the central base pairs first separate to a distance of \roodr{2.0} nm starting from an initial fully hybridized duplex. This cutoff was selected as the distance beyond \rood{which} the strands are effectively non-interacting and defines the dissociated state. \roodr{We verified that our results were robust to choices of this cutoff over the range 1.3-2.5 nm. as measured by a <7\% average deviation in rates over that range.} We extracted our computational estimate of $k_d^\mathrm{slow}$ by fitting a decaying exponential to the fraction of hybridized sequences as a function of time $f_\mathrm{hybridized}(t) = \exp(-k_d^\mathrm{slow}t)$.

@@

We present in Fig.~\ref{fig:relaxation-comparison} a comparison of $k_d^\mathrm{slow}$ and $k_d^\mathrm{fast}$ estimated by computation and experiment. Although the 3SPN.2 model was not directly fitted against kinetic data,~\cite{Hinckley2013AnHybridization} its predictions of sequence dependent T-jump relaxation rates are, within a systematic scaling factor in time and systematic shift in temperature, in good agreement with observed experimental trends. It is well-known that the smoothing of the underlying free energy landscape induced by coarse-graining artificially accelerates the kinetics of coarse-grained molecular simulations and that different degrees of freedom may be accelerated by different factors.~\citep{Marrink2007TheSimulations, Fritz2011MultiscaleDynamics, Marrink2013PerspectiveModel} We find that the simulated slow responses corresponding to center-of-mass translation of the strands during dissociation of the duplex is $\sim$10$\times$ accelerated relative to experiment, whereas the fast responses corresponding to fraying of the terminal bases is $\sim$120$\times$ accelerated. We apply these sequence-independent scaling factors to our reported computational values in Fig.~\ref{fig:relaxation-comparison}. Although the 3SPN.2 model reproduces melting temperatures relatively well, we observed a systematic 4 K under-prediction relative to experiment and so we apply a \rood{universal (+4) K corrective temperature shift} to our computational results. \roodr{We note that we would expect the model to slightly over-predict melting temperature due to the 3.5$\times$ higher concentration relative to experiment, however the systematic shift shows that relative sequence-dependent trends are well maintained. Furthermore,} We note that these empirical calibration factors to the 3SPN.2 predictions are applied only for the purposes of making an experimental comparison, but acknowledge that there are uncertainties introduced by assuming that the equilibrium dynamics at fixed temperature can be compared directly to relaxation kinetics following a 15$^\circ$C T-jump. The computational time scales and melting temperatures reported in the remainder of the paper are not \roodr{corrected by these calibration corrections} since we are only interested in the relative trends in the behaviors of the four sequences.

>>>>

All calculations were performed using the LAMMPS simulation package (\url{http://lammps.sandia.gov}) in accordance with best practices for the 3SPN.2 model. \citep{Plimpton1997FastDynamics} A single pair of self-complementary sequences were placed in a cubic periodic box with side length 7.8 nm corresponding to a single-strand concentration of \rood{7 mM}. \rood{This concentration is only 3.5$\times$ larger than the 2 mM concentration employed in our experimental analyses (Section 2.2).} Solvent effects were modeled implicitly by employing Langevin dynamics \citep{DunwegB.Paul1991BrownianNumbers., Bussi2007AccurateDynamics} with an experimentally motivated per-site friction coefficient of 9.94 $\times$ 10$^{-11}$ m$^2$/s. \citep{Nkodo2001DiffusionElectrophoresis, Hinckley2013AnHybridization} We specified a 240 mM implicit salt concentration and treated electrostatic interactions using the Debye-H{\"u}ckel with a 5 nm cutoff radius. \citep{Debye1923ZurElektrolyte} Simulations were performed in the NVT ensemble employing a Langevin thermostat. \citep{Schneider1978Molecular-dynamicsTransitions}. \rood{With the exception of the simulation data reported in Section 3.1 where we draw comparisons against experimental data collected over a range of temperatures,} each sequence was simulated at its respective melting temperature \roodr{at 7mM concentration as} dictated by the 3SPN.2 model -- AT-all: 309 K, GC-end: 317 K, GC-core: 324 K, GC-mix: 324 K -- in order to maximize the number of spontaneous transitions between dissociated and hybridized states. Melting temperatures for each sequence were determined empirically by comparing the ratio of hybridized to dissociated populations over a 10 K temperature ramp centered on the nearest neighbor (NN) model predicted melting temperature,~\citep{SantaLucia1998AThermodynamics, Santalucia2004TheMotifs} and selecting the temperature at which the hybridized and dissociated populations were approximately equal. The Langevin equations of motion were integrated using the scheme of Bussi and Parrinello \citep{Bussi2007AccurateDynamics} with a 20 fs integration time step. We performed 40 independent simulations for each of the four sequences with half of the runs initialized from the hybridized state and half from the dissociated state. The initial hybridized state was defined based on the crystal structure coordinates of Arnott et al.~\citep{Arnott1976CRCBiology} The dissociated state was generated from the hybridized state by displacing one strand away from the other by 1 nm in each of the $x$, $y$, and $z$ directions. The magnitude of this displacement did not affect the results so long as all native Watson-Crick (WC) bonds were completely broken. Initial bead velocities were assigned from a Maxwell-Boltzmann distribution at the temperature of interest. Each simulation was conducted for 26 $\mu$s and frames saved to disc every 100 ps. Each simulation required $\sim$24 CPU-hours on 28$\times$Intel E5-2680v4 CPU cores. The first 1 $\mu$s of each run was discarded for equilibration providing us with 40$\times$25 $\mu$s = 1 ms of simulation data for each sequence, during which time we observed 55-100 hybridization/dehybridization events.

@@

To computationally mimic the T-jump process in our 3SPN.2 simulations, we conducted 1 $\mu$s simulations of an initially hybridized DNA duplex over a range of temperatures and monitored its structural relaxation. We performed 120 independent simulations for each DNA sequence at each temperature, and from these extracted computational estimates of $k_d^\mathrm{slow}$ and $k_d^\mathrm{fast}$ (\blauw{Fig.~S4}). First, we tracked the slow response corresponding to duplex dissociation in our simulations by compiling the distribution of times at which both of the central base pairs first separate to a distance of \roodr{2.0} nm starting from an initial fully hybridized duplex. This cutoff was selected as the distance beyond \rood{which} the strands are effectively non-interacting and defines the dissociated state. We extracted our computational estimate of $k_d^\mathrm{slow}$ by fitting a decaying exponential to the fraction of hybridized sequences as a function of time $f_\mathrm{hybridized}(t) = \exp(-k_d^\mathrm{slow}t)$. \roodr{We verified that our cutoff was sufficiently large by observing that our calculated values for $k_d^\mathrm{slow}$ changed by an average of only 7\% by adopting a 1.3 nm cutoff.}

@@

We present in Fig.~\ref{fig:relaxation-comparison} a comparison of $k_d^\mathrm{slow}$ and $k_d^\mathrm{fast}$ estimated by computation and experiment. Although the 3SPN.2 model was not directly fitted against kinetic data,~\cite{Hinckley2013AnHybridization} its predictions of sequence dependent T-jump relaxation rates are, within a systematic scaling factor in time and systematic shift in temperature, in good agreement with observed experimental trends. It is well-known that the smoothing of the underlying free energy landscape induced by coarse-graining artificially accelerates the kinetics of coarse-grained molecular simulations and that different degrees of freedom may be accelerated by different factors.~\citep{Marrink2007TheSimulations, Fritz2011MultiscaleDynamics, Marrink2013PerspectiveModel} We find that the simulated slow responses corresponding to center-of-mass translation of the strands during dissociation of the duplex is $\sim$10$\times$ accelerated relative to experiment, whereas the fast responses corresponding to fraying of the terminal bases is $\sim$120$\times$ accelerated. We apply these sequence-independent scaling factors to our reported computational values in Fig.~\ref{fig:relaxation-comparison}. Although the 3SPN.2 model reproduces melting temperatures relatively well, we observed a systematic 4 K under-prediction relative to experiment and so we apply a \rood{universal (+4) K corrective temperature shift} to our computational results. \roodr{We note that our simulations are expected to slightly over-predict the melting temperature since they are conducted at 3.5$\times$ higher concentration relative to experiment, and the concentration-adjusted corrective shift accounting for the approximations inherent in the 3SPN.2 model would be slightly larger. Owczarzy et al.\ present an analytical prescription to apply concentration corrections to the melting temperature using knowledge of the enthalpy changes associated with duplex formation and helix nucleation \cite{Owczarzy1997predicting}. In the absence of these quantities, one could instead empirically estimate concentration corrected melting temperatures by conducting a suite of simulations over a range of temperatures and assume ideal molecular behavior to apply concentration corrections to the observed hybridized fractions \cite{Ouldridge2010ExtractingSimulations}. (As demonstrated by Ouldridge et al., finite-size corrections do not affect the melting temperature for homodimers \cite{Ouldridge2010ExtractingSimulations}.) Furthermore, we} note that these empirical calibration factors to the 3SPN.2 predictions are applied only for the purposes of making an experimental comparison, but acknowledge that there are uncertainties introduced by assuming that the equilibrium dynamics at fixed temperature can be compared directly to relaxation kinetics following a 15$^\circ$C T-jump. The computational time scales and melting temperatures reported in the remainder of the paper are not corrected by these calibration corrections since we are only interested in the relative trends in the behaviors of the four sequences.
